Multi-Robot Probabilistic Mapping and Exploration

### 2018-06-26 Dissertation/Thesis/tex/multivehicle.tex
finished chap 5, but I need to generate figs @ 2 min for patrol (3x3 grid of subfigs needs 1 more)

\subsection{Multi-Vehicle Exploration Numerical Simulation}
% Multi-vehicle ICRA figs 3-6 (remake fig. 5 with larger contrast)

@@

%	
%	\begin{figure}
%	% trim={<left> <lower> <right> <upper>}
%		\centering{
%			\subfigure[$0$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_0min.jpg}}
%			\hspace*{0.025\columnwidth}
%			\subfigure[$1$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_1min.jpg}}
%		}
%		\vspace*{0.025\columnwidth}
%		\centering{
%			\subfigure[$2$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_2min.jpg}}
%			\hspace*{0.025\columnwidth}
%			\subfigure[$3$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_3min.jpg}}
%		}
%		\vspace*{0.025\columnwidth}
%		\centering{
%			\subfigure[$4$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_4min.jpg}}
%			\hspace*{0.025\columnwidth}
%			\subfigure[$5$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_5min.jpg}}
%		}
%		\vspace*{0.025\columnwidth}
%		\centering{
%			\subfigure[$6$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_6min.jpg}}
%			\hspace*{0.025\columnwidth}
%			\subfigure[$7$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_7min.jpg}}
%		}
%		\vspace*{0.025\columnwidth}
%		\centering{
%			\subfigure[$8$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_8min.jpg}}
%			\hspace*{0.025\columnwidth}
%			\subfigure[$9$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_9min.jpg}}
%		}
%		\vspace*{0.025\columnwidth}
%		\caption{2D Projected Occupancy Grid Map of SEH Second Floor}
%			\label{fig:sim2Dmaps}
%	\end{figure}

@@

\subsection{Multi-Vehicle Patrol Numerical Simulation}
% JINT18 fig. 10-13 (ref. ICRA fig 3 from above in this chapter)

@@

>>>>

\subsection{Multi-Vehicle Exploration Numerical Simulation}
\label{sec:MultivehicleExplorationSEH}
% Multi-vehicle ICRA figs 3-6 (remake fig. 5 with larger contrast)

@@

@@

\subsection{Multi-Vehicle Patrol Numerical Simulation}
\label{sec:MultivehiclePatrolSEH}
% JINT18 fig. 10-13 (ref. ICRA fig 3 from above in this chapter)

In this section, we present a multi-vehicle exploration simulation that is identical to the scenario in Section \ref{sec:MultivehicleExplorationSEH}, except for two key differences. The first is that patrol is included in the exploration scheme to incentivize the robots to revisit areas after time passes. The second is that the robots must handle a human is walking around the space, unknown to the cooperating robots, requiring the receding horizon framework to avoid collisions with this dynamic obstacle.

\paragraph{Degradation Thread}
An additional thread within the mapping node handles cell degradation with $\lambda=1\times10^{-3}$, which corresponds to a cell half life of roughly $11.5$ minutes; if this time passes since a measurement captures a cell, the occupancy probability will be halfway between its value $11.5$ minutes ago and $P_\infty=P_\text{init}=0.1$. While degrading cells with \refeqn{CellDegradationScalar} is inexpensive, degradation must cycle through all cells, which can be costly with a map containing over $45$ million cells. Since all cells are affected by degradation, simply sending the map \emph{changes} from measurement scan updates alone is insufficient for the exploration node to track these changing probabilities. Thus, the complete map is sent from this mapping thread, and an additional thread in the exploration node subscribes to this message to update the projected map $m_\text{2D}$ slowly. The sluggish speed of this thread is acceptable, as cell degradation is a slow process, so fast updates are uncritical. Both the mapping and exploration nodes require an additional thread for degradation.

\paragraph{Simulated Results}

In the simulation, three quadrotors explore and patrol the same simulated environment from Section \ref{sec:MultivehicleExplorationSEH} of The George Washington University's (GWU) Science and Engineering Hall (SEH) for $15$ minutes while taking measurements. Initially, the robots are given no information about the environment except that their immediate surroundings are free. Unknown to the robot team, a simulated human walks in a rectangular repeated pattern at $0.5$ m/s. The 3D occupancy grid maps are shown in Fig. \ref{fig:Sim3DMapPatrol}, and the corresponding 2D projected maps for exploration are shown in Fig. \ref{fig:Sim2DMapPatrol}. The full video of both maps is available at \href{https://youtu.be/bsLG2romP_8}{\WriteBlue{https://youtu.be/bsLG2romP\_8}}.

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$2$ min}% TODO: generate this figure!
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_11min.jpg}
        		\caption{$11$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_13min.jpg}
        		\caption{$13$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_15min.jpg}
        		\caption{$15$ min}
    	\end{subfigure}
	}
	\caption{The 3D occupancy grid map representation of the SEH second floor is shown during patrol. The robots generate these maps while avoiding collisions with each other, the environment, and a non-cooperative human.}
	\label{fig:Sim3DMapPatrol}
\end{figure}

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$2$ min}% TODO: generate this figure!
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_11min.jpg}
        		\caption{$11$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_13min.jpg}
        		\caption{$13$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_15min.jpg}
        		\caption{$15$ min}
    	\end{subfigure}
	}
	\caption{The 2D projected map from of the SEH second floor shows degradation while robots patrol the space. The robots evade the non-cooperative human walking in a rectangular pattern, occasionally capturing the temporarily-occupied space and identifying these cells as occupied on the grid.}
	\label{fig:Sim2DMapPatrol}
\end{figure}

The robot generated a fairly-complete occupancy grid within $9$ minutes, and proceeded to patrol the space during the remaining time. After $9$ minutes, the total map entropy no longer increases or decreases significantly; the rate of cell degradation is roughly equal and opposite to improvements to the probabilistic map from the robot team. In contrast, if the robots simply hover instead of patrol after $9$ minutes, the map uncertainty quickly increases, shown in Fig. \ref{fig:DegradeExamples}. Furthermore, the receding horizon framework minimizes time between exploration updates, which allows the robots quickly react to dynamic obstacles like the non-cooperative human, shown in Fig. \ref{fig:EvadeHuman}.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{entropy_patrol_9minSwitch.pdf}
\caption{Total map entropies are tracked for separate trials: patrol of the building for $15$ minutes (blue) and patrol of the building for $9$ minutes, then hover (red). Even though the map is fairly well-known after $9$ minutes in either case, the continuous effort of patrolling over the complete time period shows lower map uncertainty beyond this time as cells are constantly degrading.}
\label{fig:DegradeExamples}
\end{figure}

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={22cm 25cm 20cm 0cm}, clip, width=\textwidth]{evade_15sec.jpg}
        		\caption{$15$ sec}
    	\end{subfigure}
	\hspace*{0.02\textwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={22cm 25cm 20cm 0cm}, clip, width=\textwidth]{evade_16sec.jpg}
        		\caption{$16$ sec}
    	\end{subfigure}
	\hspace*{0.02\textwidth}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim={22cm 25cm 20cm 0cm}, clip, width=\textwidth]{evade_17sec.jpg}
        		\caption{$17$ sec}
    	\end{subfigure}
	\caption{A cooperating robot must evade a non-cooperative human. The receding horizon framework allows a quickly-updating map to modify the exploration commands to avoid collisions with a dynamic obstacle.}
	\label{fig:EvadeHuman}
\end{figure}

The results also demonstrate an interesting tradeoff between exploring new terrain and patrolling previously-visited spaces. When the degradation rate $\lambda$ is increased, grid cells are degrading faster, incentivizing the exploration strategy to revisit spaces faster. This behavior is beneficial for frequent patrol, but certain areas, particularly those difficult to reach, are not visited as quickly or as frequently. Should an area receive extra attention, a greater value of $\lambda$ may be applied to this region.

@@

This chapter introduced a bidding-based framework for cooperative autonomous exploration and patrol. These contributions exploit the values of the objective functions used in autonomous exploration optimizations for a bids over a series of auctions. Between auctions, a copy of the map and collision criteria are updated, thereby coordinating the exploration efforts. Finally, a patrol scheme is developed based on simple cell degradation, promoting periodic visitations to the same regions over time.
